FraCaS: Temporal Analysis

### 2021-02-01 paper2020/paper.tex
minor_reiew
remove scitepress
typography
Use IWCS style files

\documentclass[a4paper,twoside]{article}

\usepackage{subcaption}
% \usepackage{calc}
\usepackage{natbib}
\usepackage{tabularx}
\usepackage{times}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage{todonotes}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{url}
\usepackage[capitalize]{cleveref}
\usepackage[verbose]{newunicodechar}
\input{../PaperTools/latex/newunicodedefs}
\usepackage{SCITEPRESS}     % Please add other packages that you may need BEFORE the SCITEPRESS.sty package.

@@

\title{FraCaS: Temporal Analysis}
\author{\ifanon Anonymous for review\else
  \authorname{Jean-Philippe Bernardy} \authorname{Stergios Chatzikyriakidis}
  \affiliation{University of Gothenburg}
  \email{firstname.lastname@gu.se}\fi}

\keywords{Temporal Semantics, Type-Theory}

\abstract{In this paper, we propose an implementation of temporal semantics
  which is suitable for inference problems. This implementation
  translates syntax trees to logical formulas, suitable for
  consumption by the Coq proof assistant. We support several phenomena
  including: temporal references, temporal adverbs, aspectual classes
  and progressives.  We apply these semantics to the complete FraCaS testsuite.
  We obtain an accuracy of 81 percent overall and 73 percent for problems explicitly marked
  as related to temporal reference.
}

\onecolumn \maketitle \normalsize \setcounter{footnote}{0} \vfill

@@

\onelingex{A scandinavian won the nobel prize.\label{ex:nobel}
\\
{\small\begin{multline*}
\varid{useCl}\, \varid{past}\, \varid{pPos}\\ (\varid{predVP}\, (\varid{detCN}\, (\varid{detQuant}\, \varid{indefArt}\, \varid{numSg})\\ \varid{scandinavian\_CN})\\ (\varid{complSlash}\, (\varid{slashV2a}\, \varid{win\_V2})\\ (\varid{detCN}\, (\varid{detQuant}\, \varid{indefArt}\, \varid{numSg})\\ \varid{nobel\_prize\_CN})))
\end{multline*}
}}
%
In our semantics we deal only with present and past tenses (simple and
continuous). Indeed we find that FraCas does not exercise additional
specific tenses. (When a more complicated tense is used, the
additional information is also carried by adverbs or adverbial
phrases, in a more specific way). While we believe that many other
tenses can be captured under the same general framework, we leave a
detailed study to further work.

@@

\item[existentially quantifying] The majority of temporal adverbs
  existentially quantify over a timespan. Examples include ``since
  1991'', ``in 1996'', ``for two years'', etc. The common theme is to
  introduce the interval and then restrict its bounds or its duration
  in some way. Sometimes the restriction is an equality, as in ``for
  exactly two hours''. In the following example we show the inclusion
  constraint, for ``in 1992''.

  \begin{multline*}
  ⟦\text{in 1992, \(s\)}⟧(\anyspan) = \\ ∃t_1,t_2.  [t_1,t_2] ⊆ 1992, ⟦s⟧(t_1,t_2)
\end{multline*}
In the FraCaS test suite, we normally do not find several
time-modifying adverbs modifying a single verb phrase. Indeed, sentences such
as ``in 1992, in 1991 john wrote a novel'' are infelicitous. This
justifies ignoring the input timespan in the above interpretation --
we are in particular not interested in modelling felicity with our
semantics, only giving an accurate semantics when the input is
felicitous.
\item[universally quantifying] A few adverbs introduce intervals via a
  universal quantification (sometimes with a constraint). Examples
  include ``always'' and ``never''.

@@

To be able to conclude that there is entailment, as the testsuite expects, we have to make sure
that the two occurrences of ``Jones left'' (in \textbf{P1} and \textbf{P2}) refer to the
same time intervals.
%
For this purpose we postulate \emph{unicity of action} for certain time-dependent
propositions:

\begin{multline}
  \constant{unicity}_P : P (t_1,t_2) → P (t_3,t_4) → \\ (t_1 = t_3) ∧ (t_2 = t_4)
  \label{eq:unicity}
\end{multline}

@@

\paragraph{Statives}
\textit{A contrario}, if \(P\) is \emph{stative}, then we get a time-interval subsumption property:

\begin{multline*}
\constant {subsumption}_P :\\ [t_3,t_4] ⊆ [t_1,t_2] → P (t_1,t_2) → P (t_3,t_4)
\end{multline*}
This principle is used to reason about problem (314), below:

@@

The final class of lexemes carrying a temporal-dependent semantics are
verbs taking a proposition as argument, like ``finish'', ``start'',
etc. These verbs modify the temporal context in non-trivial
ways. Consider for example ``finish to ...''. The timespan of the
argument of ``finish'' should end within the timespan of the finishing
action:

\begin{multline*}
⟦\text{finish to \(s\)}⟧(t_0,t_1) = \\ ∃(t_0',t_1'). t_1' ∈ [t_0,t_1] ∧ ⟦s⟧(t_0',t_1')
\end{multline*}

@@

\begin{figure*}
\begin{subfigure}{0.5\textwidth}

\fracasex{252}{\answer yes
\item	Since 1992 ITEL has been in Birmingham.
\item	It is now 1996.
\hyp    Itel was in Birmingham in 1993.
} \fracasex{260	}{\answer yes
\item	Yesterday APCOM signed the contract.
\item	Today is Saturday, July 14th.
\hyp    APCOM signed the contract Friday, 13th.

} \fracasex{262	}{\answer yes
\item	Smith left after Jones left.
\item	Jones left after Anderson left.
\hyp    Smith left after Anderson left.

} \fracasex{312	}{\answer yes
\item	ITEL always delivers reports late.
\item	In 1993 ITEL delivered reports.
\hyp    ITEL delivered reports late in 1993.

} \fracasex{320	}{\answer yes
\item	When Jones got his job at the CIA, he knew that he would never be allowed to write his memoirs.
\hyp    It is the case that Jones is not and will never be allowed to write his memoirs.
}

  \caption{Selected correctly handled examples}
  \label{fig:correct-examples}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
{
} \fracasex{259	}{\answer yes
\item	The conference started on July 4th, 1994.
\item	It lasted 2 days.
\hyp    The conference was over on July 8th, 1994.
\failsf Incorrect lexical semantics for ``last $n$ days''.
} \fracasex{294	}{\answer yes
\item	Smith was running his own business in two years.
\hyp    Smith ran his own business.
\failsf Parsing error for ``in two years''
} \fracasex{317	}{\answer yes
\item	Every representative has read this report.
\item	No two representatives have read it at the same time.
\item	No representative took less than half a day to read the report.
\item	There are sixteen representatives.
\hyp    It took the representatives more than a week to read the report.
\failsf Counting semantics not implemented
% } \fracasex{318	}{\answer no
% \item	While Jones was updating the program, Mary came in and told him about the board meeting.
% \item	She finished before he did.
% \hyp    Mary's story lasted as long as Jones's updating the program.
% \failsf Incorrect interaction with anaphora
}
  \caption{Selected incorrectly handled examples.
  We list below a number of selected examples from the temporal section
of the FraCaS testsuite where our semantics fails to list the correct
inference. We list the reason why it fails under the item \textbf{F}.
}
  \label{fig:incorrect-examples}
\end{subfigure}
% \caption{Selected examples.}
\end{figure*}

@@

\section*{Acknowledgements}

\ifanon
Anonymized
\else
The research reported in this paper was supported by grant 2014-39 from the
Swedish Research Council, which funds the Centre for Linguistic Theory and
Studies in Probability (CLASP) in the Department of Philosophy, Linguistics,
and Theory of Science at the University of Gothenburg. We are grateful to
our colleagues in CLASP for helpful discussion of some of the ideas presented
here. We also thank anonymous reviewers for their useful comments on an
earlier draft of the paper.
\fi
\bibliographystyle{apalike}

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2021}
\usepackage{times}
\usepackage{latexsym}
\renewcommand{\UrlFont}{\ttfamily\small}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\usepackage{subcaption}
% \usepackage{calc}
\usepackage{natbib}
\usepackage{tabularx}
\usepackage{times}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage{todonotes}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{url}
\usepackage[capitalize]{cleveref}
\usepackage[verbose]{newunicodechar}
\input{../PaperTools/latex/newunicodedefs}
% \usepackage{SCITEPRESS}     % Please add other packages that you may need BEFORE the SCITEPRESS.sty package.

@@

\title{FraCaS: Temporal Analysis}
% \author{\ifanon Anonymous for review\else
%   \authorname{Jean-Philippe Bernardy} \authorname{Stergios Chatzikyriakidis}
%   \affiliation{University of Gothenburg}
%   \email{firstname.lastname@gu.se}\fi}

\author{\ifanon Anonymous for review\else
  {Jean-Philippe Bernardy}\footnote{University of Gothenburg} ~~ {Stergios Chatzikyriakidis}\footnote{University of Gothenburg}
}

\maketitle

% \keywords{Temporal Semantics, Type-Theory}

\begin{abstract}
In this paper, we propose an implementation of temporal semantics
  which is suitable for inference problems. This implementation
  translates syntax trees to logical formulas, suitable for
  consumption by the Coq proof assistant. We support several phenomena
  including: temporal references, temporal adverbs, aspectual classes
  and progressives.  We apply these semantics to the complete FraCaS testsuite.
  We obtain an accuracy of 81 percent overall and 73 percent for problems explicitly marked
  as related to temporal reference.
\end{abstract}

% \onecolumn \maketitle \normalsize \setcounter{footnote}{0} \vfill

@@

\onelingex{A scandinavian won the nobel prize.\label{ex:nobel}
{\small\begin{multline*}
\varid{useCl}\, \varid{past}\, \varid{pPos}\\ (\varid{predVP}\, (\varid{detCN}\, (\varid{detQuant}\, \varid{indefArt}\, \varid{numSg})\\ \varid{scandinavian\_CN})\\ (\varid{complSlash}\, (\varid{slashV2a}\, \varid{win\_V2})\\ (\varid{detCN}\, (\varid{detQuant}\, \varid{indefArt}\, \varid{numSg})\\ \varid{nobel\_prize\_CN})))
\end{multline*}
}}
%
In our semantics we deal only with present and past tenses (simple and
continuous). Indeed we find that FraCas does not exercise additional
specific tenses. (When a more complicated tense is used, the
additional information is also carried by adverbs or adverbial
phrases, in a more specific way). While we believe that many other
tenses can be captured under the same general framework, we leave a
detailed study to further work.

@@

\item[existentially quantifying] The majority of temporal adverbs
  existentially quantify over a timespan. Examples include ``since
  1991'', ``in 1996'', ``for two years'', etc. The common theme is to
  introduce the interval and then restrict its bounds or its duration
  in some way. Sometimes the restriction is an equality, as in ``for
  exactly two hours''. In the following example we show the inclusion
  constraint, for ``in 1992''.
%
  \begin{multline*}
  ⟦\text{in 1992, \(s\)}⟧(\anyspan) = \\ ∃t_1,t_2.  [t_1,t_2] ⊆ 1992, ⟦s⟧(t_1,t_2)
\end{multline*}
In the FraCaS test suite, we normally do not find several
time-modifying adverbs modifying a single verb phrase. Indeed, sentences such
as ``in 1992, in 1991 john wrote a novel'' are infelicitous. This
justifies ignoring the input timespan in the above interpretation --
we are in particular not interested in modelling felicity with our
semantics, only giving an accurate semantics when the input is
felicitous.
\item[universally quantifying] A few adverbs introduce intervals via a
  universal quantification (sometimes with a constraint). Examples
  include ``always'' and ``never''.

@@

To be able to conclude that there is entailment, as the testsuite expects, we have to make sure
that the two occurrences of ``Jones left'' (in \textbf{P1} and \textbf{P2}) refer to the
same time intervals.
%
For this purpose we postulate \emph{unicity of action} for certain time-dependent
propositions:
%
\begin{multline}
  \constant{unicity}_P : P (t_1,t_2) → P (t_3,t_4) → \\ (t_1 = t_3) ∧ (t_2 = t_4)
  \label{eq:unicity}
\end{multline}

@@

\paragraph{Statives}
\textit{A contrario}, if \(P\) is \emph{stative}, then we get a time-interval subsumption property:
\begin{multline*}
\constant {subsumption}_P :\\ [t_3,t_4] ⊆ [t_1,t_2] → P (t_1,t_2) → P (t_3,t_4)
\end{multline*}
This principle is used to reason about problem (314), below:

@@

The final class of lexemes carrying a temporal-dependent semantics are
verbs taking a proposition as argument, like ``finish'', ``start'',
etc. These verbs modify the temporal context in non-trivial
ways. Consider for example ``finish to ...''. The timespan of the
argument of ``finish'' should end within the timespan of the finishing
action:
\begin{multline*}
⟦\text{finish to \(s\)}⟧(t_0,t_1) = \\ ∃(t_0',t_1'). t_1' ∈ [t_0,t_1] ∧ ⟦s⟧(t_0',t_1')
\end{multline*}

@@

@@

\ifanon

\else
\section*{Acknowledgements}
The research reported in this paper was supported by grant 2014-39 from the
Swedish Research Council, which funds the Centre for Linguistic Theory and
Studies in Probability (CLASP) in the Department of Philosophy, Linguistics,
and Theory of Science at the University of Gothenburg. We are grateful to
our colleagues in CLASP for helpful discussion of some of the ideas presented
here. We also thank anonymous reviewers for their useful comments on an
earlier draft of the paper.
\fi
\bibliographystyle{apalike}
